RNAseq aCRY pCRY data dive

### 2024-04-22 2_A_dive_aCRY_pCRY/2_A_dive_aCRY_pCRY.Rmd
local copy macbook

---
title: "RNAseq aCRY pCRY data dive"
author: "Kelterborn"
date: "2024-04-19"
output:
  github_document:
    html_preview: false
    toc: true
always_allow_html: true
editor_options: 
  chunk_output_type: console
knit: (function(input_file, encoding) {
    })
    rmarkdown::render(input_file,output_file= 'Readme.md')
---

@@

# 3. Results

## Plot Counts
```{r}

@@

@@

@@

@@

@@

### combine L2FC with padj
```{r}

@@

```{r}
outdir
figures <- paste(outdir,"figures",sep="/")
dir.create(figures)

@@

## Colours
```{r}
Greys <- brewer.pal(9, name="Greys")[c(7,5)]
Paired <- brewer.pal(12, name="Paired")[c(2,1,6,5)]
colours <- c(Greys,Paired)
```

## PCA (Panel B)
```{r}
library("PCAtools")
library(ggalt)

@@

## Counts
```{r}

@@

## Volcanos
### dark
```{r}

@@

### blue
```{r}

@@

### red
```{r}

@@

### all
```{r}

@@

### plot heatmap
```{r}
library("pheatmap")
ntd <- normTransform(dds)
top.all.hm <- head(top.all, n=100)
df <- assay(ntd)[rownames(top.all.hm),]
rownames(df) <- mcols(dds)[rownames(df),"id.symbol"]

@@

### Complex Heatmap
```{r}

@@

```{r}

>>>>

---
title: "RNAseq aCRY pCRY data dive"
author: "Kelterborn"
date: "2024-04-19"
output:
  github_document:
    html_preview: false
    toc: true
always_allow_html: true
editor_options: 
  chunk_output_type: console
knit: (function(input_file, encoding) {
    rmarkdown::render(input_file,output_file= 'Readme.md')
        })
---

@@

# 3. Results
## Colors
```{r}
# colours
Greys <- brewer.pal(9, name="Greys")[c(7,5)]
Paired <- brewer.pal(12, name="Paired")[c(2,1,6,5)]
colours <- c(Greys,Paired)
group.colors <- colours
group.colors <- c("#525252", "#969696", "#1F78B4", "#A6CEE3", "#E31A1C", "#FB9A99")
group.colors <- c("grey10","grey40","grey80","royalblue4","royalblue2", "lightblue2",  "darkred","brown2","salmon1")

anno_colors <- list(treatment = c("grey30","skyblue1","lightcoral"), #,"ivory","yellow1","gold"
                    genotype = c("green4","orchid","tan2"))

group.colours2 <- c("#00B500","#007E56","#805B00","#FF00AB","#8024AB","#FF0056","tan2","brown","orangered")

## Plot Counts
```{r plot_counts}

@@

goi <- anno_tf
l <- nrow(goi)
all_counts <- {}
for (i in 1:l){
  d <-  plotCounts(dds, gene=goi[i,"gene_id"], intgroup=c("condition","experiment","treatment","genotype"), col=col,main=res$SYMBOL[i],returnData=TRUE)
  d$Gene <- rep(goi[i,"geneSymbol"],length(rownames(d)))
  d$sample <- rownames(d)
  rownames(d) <- {}
  all_counts <- bind_rows(all_counts,d)
  }

@@

max_val <- 1.0*max(all_counts$count)

# Plot
gcounts1 <- ggplot(all_counts, aes(x = Gene, y = count, fill=condition)) +
  geom_boxplot(fatten = 1) +
  scale_fill_manual(values = group.colors) +
  scale_y_continuous(trans = "log2")
gcounts1

gcounts2 <- ggplot(all_counts, aes(x = Gene, y = count, fill=genotype)) +
  geom_boxplot(fatten = 1) +
  scale_fill_manual(values = anno_colors$genotype) +
  scale_y_continuous(trans = "log2")
gcounts2

gcounts1 / gcounts2

# ggsave(paste(figures,"2023_12_counts_tfs_aio_log2.pdf",sep="/"), plot = gcounts,
# width = 12,
# height = 8)

@@

goi <- anno_phot
l <- nrow(goi)
all_counts <- {}
for (i in 1:l){
  d <-  plotCounts(dds, gene=goi[i,"gene_id"], intgroup=c("condition","experiment","treatment","genotype"), col=col,main=res$SYMBOL[i],returnData=TRUE)
  d$Gene <- rep(goi[i,"geneSymbol"],length(rownames(d)))
  d$sample <- rownames(d)
  rownames(d) <- {}
  all_counts <- bind_rows(all_counts,d)
  }

@@

# Plot
max_val <- 1.0*max(all_counts$count)
gcounts1 <- ggplot(all_counts, aes(x = Gene, y = count, fill=condition)) +
  geom_boxplot(fatten = 1) +
  scale_fill_manual(values = group.colors) +
  scale_y_continuous(trans = "log2")
gcounts1

gcounts2 <- ggplot(all_counts, aes(x = Gene, y = count, fill=genotype)) +
  geom_boxplot(fatten = 1) +
  scale_fill_manual(values = anno_colors$genotype) +
  scale_y_continuous(trans = "log2")
gcounts2

gcounts3 <- ggplot(all_counts, aes(x = Gene, y = count, fill=condition)) +
  geom_boxplot(fatten = 1) +
  scale_fill_manual(values = group.colours2) +
  scale_y_continuous(trans = "log2")
gcounts3

gcounts1 / gcounts2 / gcounts3

# ggsave(paste(figures,"2023_12_counts_phots_aio_log2.pdf",sep="/"), plot = gcounts,
#   width = 12,
#   height = 8)

@@

### combine L2FC with padj
```{r, eval=FALSE}

@@

```{r, eval=FALSE}
outdir
figures <- paste(outdir,"figures",sep="/")
dir.create(figures)

@@

## Colours
```{r, eval=FALSE}
Greys <- brewer.pal(9, name="Greys")[c(7,5)]
Paired <- brewer.pal(12, name="Paired")[c(2,1,6,5)]
colours <- c(Greys,Paired)
```

## PCA (Panel B)
```{r, eval=FALSE}
library("PCAtools")
library(ggalt)

@@

## Counts
```{r, eval=FALSE}

@@

## Volcanos
### dark
```{r, eval=FALSE}

@@

### blue
```{r, eval=FALSE}

@@

### red
```{r, eval=FALSE}

@@

### all
```{r, eval=FALSE}

@@

### plot heatmap
```{r, eval=FALSE}
library("pheatmap")
ntd <- normTransform(dds)
top.all.hm <- head(top.all, n=100)
df <- assay(ntd)[rownames(top.all.hm),]
rownames(df) <- mcols(dds)[rownames(df),"id.symbol"]

@@

### Complex Heatmap
```{r, eval=FALSE}

@@

```{r, eval=FALSE}
